NEED A BETTER TITLE: A co-moving pair of bright stars \\ with very different metallicities and abundances

### 2017-04-13 paper/ms.tex
add some missing items

\begin{abstract}
  We report and discuss the discovery of a co-moving pair of bright stars,
  HD 240429 and HD 240430, with their detailed abundance measured.
  The kinematics of the two stars from Gaia proper motions and spectroscopic RVs
  are completely consistent with them co-moving in space.
  Yet, the metallicities and the abundances of XX elements between the stars
  separated by $\sim 0.6$~pc in space are very different,
  challenging the simple picture that these co-moving pairs are once wide binaries
  formed in a coeval star-forming event but now tidally stripping.
  We consider such and such scenarios of the formation of such pairs.
\end{abstract}

@@

In this section, we describe the data relevant to our discussion of the origin of the system.
The co-moving pair was initially discovered in our recent search
for co-moving pairs using the proper motions from Gaia DR1.
We refer the readers to \citealt{2016arXiv161202440O} and briefly describe the method here.
For a given pair, we performed a hypothesis test between the two hypotheses that
the two stars share the same 3D velocity vector and that they have
two independent 3D velocity vectors.
In the catalog of co-moving pairs (\citealt{2016arXiv161202440O}),
the pair that we present here was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above a relatively conservative cut of 6 that we adopt.
Additionally, we have checked that we do not find any possible additional co-moving companions
to this pair even when we lower the selection threshold to less conservative but still reasonable values.
The pair is in fact classified as a double star system independently
in Washington Double Star Catalog (\cite{2001AJ....122.3466M}).

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B} studied these two stars
with high resolution spectroscopy, and provided measurements of
15 different elements (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y)
as well as high precision radial velocities.
We provide all measurements relevant to the present discussion in Table~\ref{tab:t2}.

@@

@@

We discuss the possible origins of this pair.

@@

% planet-or-the-like engulfment
Yet another possibility is that the more metal-rich of the two stars
was recently? bombarded by something that selectively removed the depleted elements but not the others.

>>>>

\begin{abstract}
  We report and discuss the discovery of a co-moving pair of bright stars,
  HD 240429 and HD 240430, with their detailed abundances measured.
  The kinematics of the two stars from Gaia proper motions and spectroscopic RVs
  are completely consistent with them co-moving in space.
  Yet, the metallicities and the abundances of XX elements between the stars
  separated by $\sim 0.6$~pc in space are very different,
  challenging the simple picture that these co-moving pairs are once wide binaries
  formed in a coeval star-forming event but now tidally stripping.
  We consider such and such scenarios of the formation of such pairs.
\end{abstract}

@@

In this section, we describe the data relevant to our discussion of the origin of the system.
The co-moving pair was initially discovered in our recent search
for co-moving pairs using the proper motions from Gaia DR1.
We refer the readers to \citealt{2016arXiv161202440O} and briefly describe the method here.
For a given pair, we performed a hypothesis test between the two hypotheses that
the two stars share the same 3D velocity vector and that they have
two independent 3D velocity vectors.
In the catalog of co-moving pairs (\citealt{2016arXiv161202440O}),
the pair that we present here was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above a relatively conservative cut of 6 that we adopted.
Additionally, we have checked that we do not find any possible additional co-moving companions
to this pair even when we lower the selection threshold to less conservative but still reasonable values.
The pair is in fact classified as a double star system independently
in Washington Double Star Catalog (\cite{2001AJ....122.3466M}).

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B}
measured abundances of 15 different elements
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y)
of these two stars as well as high precision radial velocities
with high resolution spectroscopy.
We provide all measurements relevant to the present discussion in Table~\ref{tab:t2}.

@@

The abundance of HD 30 is peculiar on its own compared to other disk stars with
similar $[\elem{Fe}/\elem{H}]$. \todo{discuss}

@@

We discuss the possible origins of this pair.
Let us first consider scenarios in which the two stars are not actually born together.

@@

The unlikeliness of the above possibilities naturally leads us to 
consider the alternative.
What can selectively enrich XX elements in one of the two stars that are born together?

% inhomogeneity in star formation
It may be that the two stars are born at the same time from the same cloud, but
there is inhomogeneity. Highly doubtful based on
- Brewer et al. binaries that seem identical.
- other?

% rocky planets (or the like) engulfment
Yet another possibility is that the more metal-rich of the two stars
was recently? bombarded by something that selectively removed the depleted elements but not the others.
